\chapter*{Acknowledgments}\label{ch:acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

I would like to express my deepest appreciation to Prof. Barbara Rita Barricelli and Prof. Daniela Fogli for their invaluable guidance and support throughout my thesis. They have been patient, encouraging, and knowledgeable mentors who have inspired me to pursue excellence. I also appreciate the support and resources provided by the entire staff of the University of Brescia, which enabled me to complete this thesis successfully.

This journey would not have been possible without the support of my parents, who have sacrificed so much to give me the opportunity to follow my dreams. I hope to make them proud.

I owe a huge debt of gratitude to the special people in my life who have stood by me during this time. Linda, you have always been a source of joy and strength for me, and I cannot thank you enough for bearing with me during the most difficult times. I would be a very different person today without you. Alessia, Federica, and Samuele, you have been amazing travel companions and friends, and I cherish your support and encouragement across the distance that separates us. Lara, you have been a loyal and caring friend who has always helped me in times of need. Daniela, Davide, Simone, and Stefano, you have been a constant and reliable presence in these uncertain years.

Finally, I cannot forget the Collegio Lucchini, where I have spent the last seven years of my life. It has offered me incredible opportunities, experiences, and friendships that I will always treasure. I am thankful to all the people who have shared this journey with me, both the “old guard” and the newcomers. Naming them all is not easy, but I will try: Alberto, Alessandra, Alessandro, Alice, Annabell, Antonio, Barak, Bruno, Camilla, Chiara, Daniele, Dumy, Filippo, Gaia, Giada, Giaele, Giulia, Ilenia, Jozef, Marcos, Martina, Matteo, Michele Fioroni, Michele Morselli, Nicholas, Wade. I also want to recognize the staff of the Collegio: Andrea Galli, Carla Bisleri, Lorenzo Gafforini, Luigi Negretti, Marta Perrini, and Paolo Carli. Thanks also to Beatrice Faedi, who introduced me to the world of theater. You have all made this place feel like home, and it is not going to be easy to leave.

